\documentclass[11pt,letterpaper]{article}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\pagestyle{empty}

% Custom commands for section formatting
\newcommand{\namesection}[3]{
  \begin{center}
    \huge\textbf{#1}\\[4pt]
    \normalsize#2 | #3
  \end{center}
}

\titleformat{\section}
  {\Large\bfseries\uppercase}
  {}
  {0em}
  {}
  [\titlerule]

\titlespacing*{\section}{0pt}{12pt}{8pt}

\newcommand{\job}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}\\
}

\newcommand{\project}[2]{
  \textbf{#1} | #2
}

\begin{document}

\namesection{Michael Ugochukwu}
  {(682) 552-4468 | michael.buuchi@gmail.com}
  {\href{https://linkedin.com/in/michael-ugochukwu}{linkedin.com/in/michael-ugochukwu} | \href{https://github.com/Buchimi}{github.com/Buchimi}}

\section{Education}
\textbf{University of Texas at Dallas} \hfill Dallas, TX\\
Bachelor of Science in Computer Science \hfill Aug. 2021 – Dec 2024\\
GPA: 3.7

\section{Experience}
\job{Google}{Mountain View, CA}{Software Engineering Intern (Flutter, Dart)}{May 2024 – August 2024}
\begin{itemize}[leftmargin=*,nosep]
  \item Drafted a design doc, gathered approvals and created a new feature on Google's family link app.
  \item Utilized internal tooling to perform screen diffing tests in Flutter, ensuring new features work as intended.
  \item Implemented and tested new foreign function interface (FFI) package templates in languages like Go, Rust and C++ for the Flutter framework (open source).
  \item Improved Java annotations on the backend, eliminating the possibility of unexpected parameter value bugs to unset optional parameters (Dependency injection bugs)
  \item Leveraged Flutter's internal API to implement responsive animated widgets, improving in app user experience.
  \item Improved text to speech labeling on Flutter widgets, improving audio based accessibility features.
\end{itemize}

\job{Rondevu}{Dallas, TX}{Software Engineer}{Nov 2023 – Mar 2024}
\begin{itemize}[leftmargin=*,nosep]
  \item Optimized server response times by implementing clever caching techniques, leading to latency drops of 78\%.
  \item Reduced database query time from 3300 ms to 13 ms by smart index design and time dependent document processing using Redis as a message queue.
  \item Designed admin control page using NextJS and Tailwind to let admin users manually perform operations like sending notifications to users or verifying photos.
  \item Reduced server storage costs by on-server file compression, leading to a reduction of storage use by 20\%.
  \item Mentored engineering peers on front-end, back-end development and mobile development with React-Native.
\end{itemize}

\job{Rivian Automotive}{Palo Alto, CA}{Software Engineering Intern}{May 2023 – Aug 2023}
\begin{itemize}[leftmargin=*,nosep]
  \item Developed a banner feature utilizing React.JS and Material UI to notify users of internal tools/software about software status, including service downtime, platform updates, and service availability.
  \item Built microservices using Java and Spring to power the banner feature and handle CRUD operations on banner objects against a DynamoDB instance.
  \item Utilized JUnit and Mockito to write comprehensive unit tests, guaranteeing the reliability of the server and 100\% code coverage.
  \item Leveraged the DGS Graphql framework to build a Graphql monolith to support the implementation of efficient queries and mutations of database objects in Java.
  \item Devised Python scripts to resolve local repository errors, ensuring seamless codebase execution and testing.
\end{itemize}

\section{Projects}
\project{Personal Website}{React, NextJS, Typescript, NodeJS} \hfill Dec 2022 – Present
\begin{itemize}[leftmargin=*,nosep]
  \item Designed and developed a personal project showcase website using ReactJS and NextJS.
  \item Applied responsive web design that allowed the website to adapt to different screen sizes and devices
  \item Leveraged ReactJS to create engaging animations that enhanced user experience and resulted in an increase in user engagement.
\end{itemize}

\project{Interview Prep Website}{React, Firebase, Javascript, NodeJS} \hfill October 2022
\begin{itemize}[leftmargin=*,nosep]
  \item Created a web platform using NodeJS and ReactJS that prepares students for virtual interviews.
  \item Leveraged both Firebase Firestore database and storage services to store student interview videos.
  \item Designed an intuitive rating and feedback system, allowing users to provide constructive critiques and ratings for uploaded interview videos.
\end{itemize}

\section{Technical Skills}
\textbf{Languages:} Java, Python, C/C++, Javascript/Typescript, Dart, Rust\\
\textbf{Frameworks:} React, Node.js, Spring, JUnit, DGS, Material-UI, Flutter, NextJS, Tailwind, Expo/React-Native\\
\textbf{Developer Tools:} AWS, GraphQL, Git, Linux, Terraform, Firebase

\end{document}